A meta-analysis of fungicide spray schedules to minimise yield loss from powdery mildew in Australian mungbean

### 2020-07-30 07_Manuscript.Rmd
Corrections movement of figures addition of some hardcoded results

```{r MEsummary_Libraries1, message=FALSE, echo=FALSE, include=FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, kableExtra, here, flextable, officer, english)

@@

# Data
PM_Mdat <- read.csv(here("cache/PM_MB_updated.csv"))
load(file = here("cache/Meta-analysisData.Rdata"))
load(file = here("cache/PreliminaryData.Rdata"))
source(here("R/reportP.R"))
```

@@

## Materials and Methods
**Trial criteria for inclusion and description**
The data for this study were obtained through personal correspondence with colleagues and collaborating institutions.
Trials undertaken in the 2013 season were conducted by the Northern Growers Alliance (NGA) [-@goolhi2013; -@premer2013; -@Millmerran2013; -@Marysmount2013].
<!-- should check, Sue and Mal moved to USQ in 2015 I think. Therefore the trials probably started with USQ earlier --> 
Trial data were obtained in different formats with varying levels of information.
Some trials we obtained the raw data, others the reported means of each treatment, with all but one study reporting some form of variance along with the mean. 
Twenty six trials in total were collated.

To ensure the correct question was asked of the analysis, the data needed to conform to a strict criteria. 
The criteria for inclusion of trial data in the meta-analysis required, a field trial testing fungicide efficacy for powdery mildew control on mungbean in the Grains Research and Development (GRDC) northern grains regions of eastern Australia, which grows the majority of Australia's summer crops.
Trial data had to include: the date when powdery mildew was first observed; disease incidence at the end of the growing season; fungicide application dates; the fungicide active ingredients; fungicide dose; and crop yield. 
The data were subset to only include fungicide treatments with the same mode of action; demethylase inhibitor (DMI) fungicides, tebuconazole and propiconazole were thus retained in the dataset. 
Subsequently the 26 trials were reduced to 17 trials (Table 1). 
Two more trials were also removed because no form of variance was reported with the fungicide treatment means of grain yield, reducing the number of trials down to 15.

From the trials which were included `r as.english(sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 12))` planted in late December, `r as.english(sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 1))` in January and `r as.english(sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 2))` trials planted in February (Table 1).

In the meta-analysis, to ensure sufficient replication, we made no distinction between the tebuconazole and propiconazole fungicide treatments within the trials that met the selection criteria. 
The design of all trials included in this analysis were randomised complete block designs, and were not previously published in peer-reviewed literature. 
Details of trial data are presented within a research compendium which was prepared as a supplement to this publication [<!-- DOI to reference to compendium -->].

**Response variable - Grain yield**
Grain yield (tonne per hectare), was used as the response variable for the meta-analysis. 
Mean grain yields for each treatment were either obtained directly from trial reports, or calculated from the raw data when available.
The sample variance was calculated from the raw data when available or the least squares statistic in trial reports. 
Sample variance for the 2012 Kingaroy study was calculated from the reported least squares statistic using a T-critical value of 2.042 and the approach reported in Ngugi et al. [-@Ngugi2011].
The T-critical value was determined from the 30 degrees of freedom and probability of $a = 0.05$ using a t-distribution table.

@@

**Trial Variables and moderators**
While the main aim of all the identified trials were to assess the efficacy of fungicide for control of powdery mildew, some trials tested additional potential covariates in the experimental design.
These additional variables included: row spacing, fungicide active ingredient, fungicide dose, planting date, number of fungicide applications and cultivar.
To account for the variation attributed to some of these variables between trials, and within trials, a single $trial$ factor was created.
The $trial$ random variable made distinctions between the following variables: unique trial reference code, trial location, trial season, host genotype, row spacing, and fungicide dose.

@@

The timing of fungicide application treatments, were defined in relation to the recorded date when powdery mildew first occurred in the trial. 
An $Early$ fungicide application treatment, referred to a fungicide spray schedule that commenced prior to the disease being observed in the trial. 
$Recommended$ referred to a fungicide spray schedule which commenced 1 -- 3 days following the first sign of disease. 
$Late$ treatments commenced between 7 and 13 days after the first sign of disease. 
There were no spray schedule treatments which began between 4 and 6 days after the first sign of powdery mildew. 
The number of fungicide applications were binned in to two categories.
A spray schedule with a $single$ spray, and a spray schedule with two or three spray applications $plus$. 
The division of the treatments produced: 13 $Early_{single}$ treatments; 5 $Early_{plus}$; 32 $Recommended_{single}$; 46 $Recommended_{plus}$'; 17 $Late_{single}$; and 20 $Late_{plus}$.
$Early_{plus}$ treatments were removed from the subsequent meta-analysis, due to an insufficient sample size.  
What remained was the mean yield for a total of 173 treatments in the following five spray schedule categories: no spray control, single early spray, single recommended spray, recommended with multiple sprays, single late spray, and late with multiple sprays.

An ordinal 1 -- 9 ordinal scale was used to describe the mean plot powdery mildew severity in most trials (Table 2). 
However, the 2013 NGA trials (Table 1) reported incidence as the percentage of leaves covered by powdery mildew and the location of the infected leaves in the lower, middle or upper canopy. 
Given the ordinal scale ranked plants on the percent of foliage up the plant showing the disease, a conversion to mean plot severity on the ordinal 1 -- 9 scale was straight-forward. 
The end of season mean plot severity, and and date of first sign of disease were used to calculate the area under the disease progress curve (AUDPC) for each treatment. 
Additional powdery mildew mean plot severity observations made in-between these two observations were also included in the AUDPC calculation if they were available. 
AUDPC was calculated using the `agricolae` package in R [@agricolae2020]. 
A categorical disease pressure factor was created by binning trials based on the mean AUDPC of the no spray control plot into two levels: 'low disease pressure' or 'high disease pressure'.
The two levels were separated by the median AUDPC (`r as.double(read.csv(here("cache/median_AUDPC_C.csv")))`) of the no spray control plots.

Linear contrasts were used to compare the mean effect sizes between each spray schedule treatment and their respective standard errors and confidence intervals.

@@

```{r Figure2_treatForest, echo = FALSE}
YieldContrasts
```
<br>
<br>
```{r Table1_ExperimentalDetail, echo=FALSE, message=FALSE, warning=FALSE}
# Add a star to the trials which were not in the final analysis
PM_Mdat[!PM_Mdat$trial_ref %in% slimmer_PM_dat$trial_ref, "trial_ref"] <-
   sapply(PM_Mdat[!PM_Mdat$trial_ref %in% slimmer_PM_dat$trial_ref,"trial_ref"], paste0, "*")

# Build table 
PM_Mdat %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole") %>%
   group_by(trial_ref) %>%
   summarise(
      year = unique(year),
      location = unique(location),
      planting_date = unique(planting_date),
      first_sign_disease = unique(first_sign_disease)
   ) %>%
   arrange(year) %>%
   mutate(Research_org = c(
      rep("Queensland DAF", times = 4),
      rep("Northern Growers Alliance", times = 4),
      rep("Queensland DAF", times = 4),
      rep("USQ", times = 5)
   )) %>%
   flextable()%>%
   set_caption("Table 1: Description of Experiments") %>%
   set_header_labels(trial_ref = "Unique Trial Reference",
                     year = "Year",
                     location = "Trial Location",
                     planting_date = "Planting Date",
                     first_sign_disease = "First sign of disease date",
                     Research_org = "Research organisation")%>%
   autofit(add_w = 0.5)%>%
   align(j = c(1,4,5), align = "center", part = "all")%>%
   fontsize(size = 9)%>%
   width(j = 1:4, 1)%>%
   width(j = 5, 1.1)%>%
   width(j = 6, 1.7)
```
<br>
<br>
```{r Table2_1to9Scale, echo=FALSE}
data.frame(
   Scale = 1:9,
   `Scale Description` = c(
      "No sign of powdery mildew",
      "Small colonies in lower 1/3 of canopy, up to 75% of plants affected",
      "Colonies in lower 1/2 of canopy, > 75 % of plants affected",
      "Colonies in lower 2/3 of canopy, up to 75 % of plants affected",
      "Colonies in lower 2/3 of canopy, > 75 % of plants affected",
      "Colonies in lower 2/3 of canopy, 100 % of plants affected",
      "Colonies in lower 2/3 of canopy, 100 % of plants, with some plants with colonies in the top 1/3 of canopy",
      "Colonies to top of the plant with > 75 % of plants affected",
      "Colonies to top of the plant with > 100 % of plants affected and heavy leaf drop"
   )
) %>%
   flextable()%>%
   set_caption("Table 2: Powdery Mildew severity scoring scale") %>%
   set_header_labels(Scale.Description = "Scale Description")%>%
   autofit()%>%
   fontsize(size = 9)%>%
   align(j = c(1), align = "center", part = "all")%>%
   width(j = 2, 6.2)
```

@@

<!-- Write about first sign of disease in March -->
Overall the meta-analysis indicated that, with the exception of `Early` single sprays all the the spray schedules were effective at protecting mungbean yields, relative to the no spray controls (Figure 2). 
Treatments which incorporating multiple fungicide applications, `RecommendedPlus` and `LatePlus` produced the highest mean yield protection estimates at 196.4 (SE = 48.7&nbsp;kg&nbsp;/&nbsp;ha) and 219.9&nbsp;kg&nbsp;/&nbsp;ha (SE = 47.4&nbsp;kg&nbsp;/&nbsp;ha) respectively (Table 3). 
Both `RecommendedPlus` and `LatePlus` were also significantly higher than single applications starting `Early` (P = 0.008 and P = 0.003 respectively) and `Late`(P = 0.05 and P = 0.03 respectively). 
However, comparing `LatePlus` and `Early` should done with caution given these treatments did not occur within the same trial for any of the 15 trials included in the meta-analysis. 
Within the single fungicide application treatments `Recommended` provided the highest yield protection, and was estimated at saving an average of 159.9 kg / ha (SE = 30.5 kg / ha) relative to the no spray control (P < 0.0001). 
`Recommended` treatments were was also significantly higher than `Early` treatments by 122.1 kg / ha (SE = 42.1 kg / ha)(P = 0.004). 
Single `Late` applications were effective at significantly mitigating the effect of powdery mildew on yield by a mean of 122 kg / ha (SE = 39.2 kg / ha)(P = 0.0019). 
However, this estimate was not significantly different to single `Early` or `Recommended` treatments (P = 0.119; P = 0.278 respectively).

>>>>

```{r MEsummary_Libraries1, message=FALSE, echo=FALSE, include=FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, kableExtra, here, flextable, officer, english,pander)

@@

# Data
PM_Mdat <- read.csv(here("cache/PM_MB_updated.csv"))
load(file = here("cache/Meta-analysisData.Rdata"))
load(file = here("cache/PreliminaryData.Rdata"))
T3 <- read.csv(here("cache/Table3_contrasts.csv"), stringsAsFactors = FALSE)
T3[,2:5] <- round(T3[,2:5], 4)
source(here("R/reportP.R"))
```

::: {custom-style="Art_type"}
Type of Paper: Article
:::

::: {custom-style="keywords"}
**Keywords:** meta-analysis, powdery mildew, mungbean, fungicide `r print("                                                       ")`                                                     
:::
<!-- Is anyone aware of a way to put the "Type of paper" text above the renderd YAML header? ... or ... Specify extra text in the header which is rendered as a different style? 
I am considering dropping the lua files and just codeing in the different styles to suit the MDPI_Agronomy_Template.docx -->

@@

## Materials and Methods
**Trial criteria for inclusion and description :**
The data for this study were obtained through personal correspondence with colleagues and collaborating institutions.
Trials undertaken in the 2013 season were conducted by the Northern Growers Alliance (NGA) [-@goolhi2013; -@premer2013; -@Millmerran2013; -@Marysmount2013].
<!-- should check, Sue and Mal moved to USQ in 2015 I think. Therefore the trials probably started with USQ earlier --> 
Trial data were obtained in different formats with varying levels of information.
Some trials we obtained the raw data, others the reported means of each treatment, with all but one study reporting some form of variance along with the mean. 
Twenty six trials in total were collated.

To ensure the correct question was asked of the analysis, the data needed to conform to a strict criteria. 
The criteria for inclusion of trial data in the meta-analysis required, a field trial testing fungicide efficacy for powdery mildew control on mungbean in the Grains Research and Development (GRDC) northern grains regions of eastern Australia, which grows the majority of Australia's summer crops.
Data from trials undertaken in this regionhad to include: the date when powdery mildew was first observed; disease incidence at the end of the growing season; fungicide application dates; the fungicide active ingredients; fungicide dose; and crop yield. 
The data were subset to only include fungicide treatments with the same mode of action; demethylase inhibitor (DMI) fungicides, tebuconazole and propiconazole were thus retained in the dataset. 
Subsequently the 26 trials were reduced to 17 trials (Table 1). 
Two more trials were also removed because grain yield variance, which was required for the meta-analysis, was not reported, reducing the number of trials down to 15.

```{r Table1_ExperimentalDetail, echo=FALSE, message=FALSE, warning=FALSE}
# Add a star to the trials which were not in the final analysis
PM_Mdat[!PM_Mdat$trial_ref %in% slimmer_PM_dat$trial_ref, "trial_ref"] <-
   sapply(PM_Mdat[!PM_Mdat$trial_ref %in% slimmer_PM_dat$trial_ref,"trial_ref"], paste0, "*")

# Build table 
PM_Mdat %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole") %>%
   group_by(trial_ref) %>%
   summarise(
      year = unique(year),
      location = unique(location),
      planting_date = unique(planting_date),
      first_sign_disease = unique(first_sign_disease)
   ) %>%
   arrange(year) %>%
   mutate(Research_org = c(
      rep("Queensland DAF", times = 4),
      rep("Northern Growers Alliance", times = 4),
      rep("Queensland DAF", times = 4),
      rep("USQ", times = 5)
   )) %>%
   flextable()%>%
   set_caption("Table 1: Description of Experiments") %>%
   set_header_labels(trial_ref = "Unique Trial Reference",
                     year = "Year",
                     location = "Trial Location",
                     planting_date = "Planting Date",
                     first_sign_disease = "First sign of disease date",
                     Research_org = "Research organisation")%>%
   autofit(add_w = 0.5)%>%
   align(j = c(1,4,5), align = "center", part = "all")%>%
   fontsize(size = 9)%>%
   width(j = 1:4, 1)%>%
   width(j = 5, 1.1)%>%
   width(j = 6, 1.7)
```

From the trials which were included in the meta-analysis, `r as.english(sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 12))` were planted in late December, `r as.english(sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 1))` in January and `r as.english(sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 2))` were trials planted in February (Table 1).

In the meta-analysis, to ensure sufficient replication, we made no distinction between the tebuconazole and propiconazole fungicide treatments within the trials that met the selection criteria. 
The design of all trials included in this analysis were randomised complete block designs, and were not previously published in peer-reviewed literature. 
Details of trial data are presented within a research compendium as a supplement to this publication [<!-- DOI to reference to compendium -->].

**Response variable - Grain yield: **
Grain yield (tonne per hectare), was used as the response variable for the meta-analysis. 
Mean grain yields for each treatment were either obtained directly from trial reports, or calculated from the raw data when available.
The sample variance was calculated from the raw data when available or the least squares statistic in the trial reports. 
Sample variance for the 2012 Kingaroy study was calculated from the reported least squares statistic using a T-critical value of 2.042 and the approach reported in Ngugi et al. [-@Ngugi2011].
The T-critical value was obtained from a t-distribution table using, 30 degrees of freedom and probability of $a = 0.05$.

@@

**Trial Variables and moderators: **
While the main aim of all the identified trials were to assess the efficacy of fungicide for control of powdery mildew, some trials tested additional potential covariates in the experimental design.
These additional variables included: row spacing, fungicide active ingredient, fungicide dose, planting date, number of fungicide applications and cultivar.
To account for the variation attributed to some of these variables between trials, and within trials, a single $trial$ factor was created.
The $trial$ random variable made distinctions between the following variables: unique trial reference code, trial location, trial season, host genotype, row spacing, and fungicide dose.

@@

The timing of fungicide application treatments, were defined in relation to the recorded date when powdery mildew first occurred in the trial. 
An $Early$ fungicide application treatment, referred to a fungicide spray schedule that commenced prior to the disease being observed in the trial. 
$Recommended$ referred to a fungicide spray schedule which commenced 1 -- 3 days following the first sign of disease. 
$Late$ treatments commenced between 7 and 13 days after the first sign of disease. 
There were no spray schedule treatments which began between 4 and 6 days after the first sign of powdery mildew. 
The number of fungicide applications were binned in to two categories.
A spray schedule with a $single$ spray, and a spray schedule with two or three spray applications $plus$. 
The division of the treatments produced: 13 $Early_{single}$ treatments; 5 $Early_{plus}$; 32 $Recommended_{single}$; 46 $Recommended_{plus}$'; 17 $Late_{single}$; and 20 $Late_{plus}$.
$Early_{plus}$ treatments were removed from the subsequent meta-analysis, due to an insufficient sample size.  
What remained was the mean yield for a total of 173 treatments in the following five spray schedule categories: no spray $control$, $Early_{single}$, $Recommended_{single}$, $Recommended_{plus}$, $Late_{single}$, and $Late_{plus}$.

An ordinal 1 -- 9 scale was used to describe the mean powdery mildew plot severity in most trials (Table 2). 
However, the 2013 NGA trials (Table 1) reported mean plot severity as the percentage of leaves covered by powdery mildew and the location of the infected leaves in the lower, middle or upper canopy. 
Given the ordinal scale ranked plots on the percent of foliage showing the disease from the lower canopy to the upper canopy, a conversion from percentage of the diseased canopy, to the 1 -- 9 scale was straight-forward. 
The end of season mean plot severity, and date of first sign of disease were used to calculate the area under the disease progress curve (AUDPC) for each treatment. 
Additional powdery mildew mean plot severity observations made in-between these two observations were also included in the AUDPC calculation if they were available. 
AUDPC was calculated using the `agricolae` package in R [@agricolae2020]. 
A categorical disease pressure factor was created by binning trials into two levels based on the mean AUDPC of the no spray control plot.
The two levels, 'low disease pressure' and 'high disease pressure', were separated by the median AUDPC (`r as.double(read.csv(here("cache/median_AUDPC_C.csv")))`) of the no spray control plots.  
<br>
```{r Table2_1to9Scale, echo=FALSE}
data.frame(
   Scale = 1:9,
   `Scale Description` = c(
      "No sign of powdery mildew",
      "Small colonies in lower 1/3 of canopy, up to 75% of plants affected",
      "Colonies in lower 1/2 of canopy, > 75 % of plants affected",
      "Colonies in lower 2/3 of canopy, up to 75 % of plants affected",
      "Colonies in lower 2/3 of canopy, > 75 % of plants affected",
      "Colonies in lower 2/3 of canopy, 100 % of plants affected",
      "Colonies in lower 2/3 of canopy, 100 % of plants, with some plants with colonies in the top 1/3 of canopy",
      "Colonies to top of the plant with > 75 % of plants affected",
      "Colonies to top of the plant with > 100 % of plants affected and heavy leaf drop"
   )
) %>%
   flextable()%>%
   set_caption("Table 2: Powdery Mildew severity scoring scale") %>%
   set_header_labels(Scale.Description = "Scale Description")%>%
   autofit()%>%
   fontsize(size = 9)%>%
   align(j = c(1), align = "center", part = "all")%>%
   width(j = 2, 6.2)
```
<br>
The mean difference in grain yield was estimated from the difference in model estimates of the non-treated control and each of the spray schedule treatments using fungicide.  
Disease pressure was tested against the basic model to determine if, when introduced as a moderator variable, it could significantly explain additional heterogeneity between the spray schedule treatments. A a Wald-type test was used to test the impact of the disease pressure factor.

Linear contrasts were used to produce the mean difference in effect sizes, and their respective standard errors and 95&nbsp;% confidence intervals, between each spray schedule treatment.

@@

```{r Figure2_treatForest, echo = FALSE}
YieldContrasts
```

@@

Overall the meta-analysis indicated that, with the exception of the $Early_{single}$ treatment, all the the spray schedules were effective at protecting mungbean yields relative to the no spray controls (Figure 2). 
Treatments which incorporating multiple fungicide applications, $Recommended_{plus}$ and $Late_{plus}$, produced the highest mean yield protection estimates at `r round(PM_mv$b[4,1] * 1000, 2)` (SE = `r round(PM_mv$se[4] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha) and `r round(PM_mv$b[6,1] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha (SE = `r round(PM_mv$se[6] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha) respectively (Table 3). 
Both $Recommended_{plus}$ and $Late_{plus}$ were also significantly higher than single applications $Early_{single}$ (P = `r T3$pval[2]` and P = `r T3$pval[4]` respectively) and $Late_{single}$(P = `r T3$pval[8]` and P = `r T3$pval[10]` respectively). 
However, comparing $Late_{plus}$ and $Early_{single}$ should done with caution given these treatments did not occur within the same trial for any of the 15 trials included in the meta-analysis. 
Within the single fungicide application treatments `Recommended` provided the highest yield protection, and was estimated at saving an average of 159.9 kg / ha (SE = 30.5 kg / ha) relative to the no spray control (P < 0.0001). 
`Recommended` treatments were was also significantly higher than `Early` treatments by 122.1 kg / ha (SE = 42.1 kg / ha)(P = 0.004). 
Single `Late` applications were effective at significantly mitigating the effect of powdery mildew on yield by a mean of 122 kg / ha (SE = 39.2 kg / ha)(P = 0.0019). 
However, this estimate was not significantly different to single `Early` or `Recommended` treatments (P = 0.119; P = 0.278 respectively).

### 2020-07-30 vignette/Manuscript2Word.Rmd
Corrections movement of figures addition of some hardcoded results

# Data
PM_Mdat <- read.csv(here("cache/PM_MB_updated.csv"))
load(file = here("cache/Meta-analysisData.Rdata"))
load(file = here("cache/PreliminaryData.Rdata"))
source(here("R/reportP.R"))
```

@@

<!-- Write about first sign of disease in March -->
Overall the meta-analysis indicated that, with the exception of `Early` single sprays all the the spray schedules were effective at protecting mungbean yields, relative to the no spray controls (Figure 2). 
Treatments which incorporating multiple fungicide applications, `RecommendedPlus` and `LatePlus` produced the highest mean yield protection estimates at 196.4 (SE = 48.7&nbsp;kg&nbsp;/&nbsp;ha) and 219.9&nbsp;kg&nbsp;/&nbsp;ha (SE = 47.4&nbsp;kg&nbsp;/&nbsp;ha) respectively (Table 3). 
Both `RecommendedPlus` and `LatePlus` were also significantly higher than single applications starting `Early` (P = 0.008 and P = 0.003 respectively) and `Late`(P = 0.05 and P = 0.03 respectively). 
However, comparing `LatePlus` and `Early` should done with caution given these treatments did not occur within the same trial for any of the 15 trials included in the meta-analysis. 
Within the single fungicide application treatments `Recommended` provided the highest yield protection, and was estimated at saving an average of 159.9 kg / ha (SE = 30.5 kg / ha) relative to the no spray control (P < 0.0001). 
`Recommended` treatments were was also significantly higher than `Early` treatments by 122.1 kg / ha (SE = 42.1 kg / ha)(P = 0.004). 
Single `Late` applications were effective at significantly mitigating the effect of powdery mildew on yield by a mean of 122 kg / ha (SE = 39.2 kg / ha)(P = 0.0019). 
However, this estimate was not significantly different to single `Early` or `Recommended` treatments (P = 0.119; P = 0.278 respectively).

>>>>

# Data
PM_Mdat <- read.csv(here("cache/PM_MB_updated.csv"))
load(file = here("cache/Meta-analysisData.Rdata"))
load(file = here("cache/PreliminaryData.Rdata"))
T3 <- read.csv(here("cache/Table3_contrasts.csv"), stringsAsFactors = FALSE)
T3[,2:5] <- round(T3[,2:5], 4)
source(here("R/reportP.R"))
```

@@

$control$, $Early_{single}$, $Recommended_{single}$, $Recommended_{plus}$, $Late_{single}$, and $Late_{plus}$.  
Overall the meta-analysis indicated that, with the exception of the $Early_{single}$ treatment, all the the spray schedules were effective at protecting mungbean yields relative to the no spray controls (Figure 2). 
Treatments which incorporating multiple fungicide applications, $Recommended_{plus}$ and $Late_{plus}$, produced the highest mean yield protection estimates at `r round(PM_mv$b[4,1] * 1000, 2)` (SE = `r round(PM_mv$se[4] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha) and `r round(PM_mv$b[6,1] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha (SE = `r round(PM_mv$se[6] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha) respectively (Table 3). 
Both $Recommended_{plus}$ and $Late_{plus}$ were also significantly higher than single applications $Early_{single}$ (P = `r T3$pval[2]` and P = `r T3$pval[4]` respectively) and $Late_{single}$(P = `r T3$pval[8]` and P = `r T3$pval[10]` respectively). 
However, comparing $Late_{plus}$ and $Early_{single}$ should done with caution given these treatments did not occur within the same trial for any of the 15 trials included in the meta-analysis. 
Within the single fungicide application treatments `Recommended` provided the highest yield protection, and was estimated at saving an average of 159.9 kg / ha (SE = 30.5 kg / ha) relative to the no spray control (P < 0.0001). 
`Recommended` treatments were was also significantly higher than `Early` treatments by 122.1 kg / ha (SE = 42.1 kg / ha)(P = 0.004). 
Single `Late` applications were effective at significantly mitigating the effect of powdery mildew on yield by a mean of 122 kg / ha (SE = 39.2 kg / ha)(P = 0.0019). 
However, this estimate was not significantly different to single `Early` or `Recommended` treatments (P = 0.119; P = 0.278 respectively).
